Experiences with Planning for Natural Language Generation

### 2009-06-03 trunk/Papers/ci-spark/experiments.tex
changes to data and section 4

@@

\begin{figure}[t]
  \centering
  \subfloat[position=bottom][(a) Minimal world]{%
      \includegraphics[height=2.5cm,clip=true,trim=0 -10px 0 -3px]{pic-buttons}}
  \qquad
  \subfloat[position=bottom][(b) Extra grid cells with accessible positions]{%
      \includegraphics[height=2.5cm]{pic-empty-buttons}} \\
  \subfloat[(c) Extra grid cells with inaccessible positions]{%
      \includegraphics[height=2.5cm]{pic-empty-inaccessible}}
  \caption{Experimental GIVE world configuration.}
  \label{fig:give-maps}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.75\columnwidth]{graph-exp2}
  %\includegraphics[width=1\columnwidth]{pic-runtime-buttons}
  \caption{Results on the minimal GIVE
    domain for $h=20$. The horizontal axis is $n$. The vertical axis
    is the runtime in seconds.}
  \label{fig:give-runtime-minimal}
\end{figure}

@@

Results for the $h=20$, $n=5$ case with $w$ ranging from $1$ to $70$ are
shown in Figure~\ref{fig:give-runtime-junk}. As in Experiment~2, FF again
runs out of memory, this time at $w=17$, while SGPLAN easily solves inputs
beyond $w=70$. As in Experiment~2, our implementation of GraphPlan is
unable to generate any of these plans. Unlike Experiment 2, however, both
FF and SGPLAN now spend a substantial proportion of their time on
grounding. In SGPLAN, this translates to a ``parsing time'' (which we
assume includes grounding) which grows from 180 ms to 21.7 seconds as $w$
grows from $1$ to $75$. The rest of the runtime, which also includes the
search time, only grows from 400 ms to 2.3 seconds. This difference is
particularly dramatic given that the actual optimal plan in each case is an
identical plan of about 100 steps (i.e., the one we would have found in
Experiment 2 for the $h=20$, $n=5$ case). The planning times for these
instances are also concerning since times over a couple seconds will
negatively affect the overall response time of the system, which must react
in real time to user actions.

\begin{figure}[t]
  \centering
  \includegraphics[width=0.75\columnwidth]{graph-exp3}
  %\includegraphics[width=1\columnwidth]{pic-runtime-empty-world}
  \caption{Results on the GIVE domain with junk
    positions for $h=20$ and $n=5$. The horizontal axis is $w$.
    The vertical axis is the runtime in seconds.}
  \label{fig:give-runtime-junk}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \subfloat[position=bottom][(a) Minimal world]{%
      \includegraphics[height=2.5cm,clip=true,trim=0 -10px 0 -3px]{pic-buttons}}
  \qquad
  \subfloat[position=bottom][(b) World with extra grid cells]{%
      \includegraphics[height=2.5cm]{pic-empty-buttons}} \\
  %\subfloat[(c) Extra grid cells with inaccessible positions]{%
  %    \includegraphics[height=2.5cm]{pic-empty-inaccessible}}
  \caption{Experimental GIVE world configurations.}
  \label{fig:give-maps}
\end{figure}

@@

@@

\begin{figure}[t]
\subfloat[(a) Unordered]{\includegraphics[width=7cm]{data/give-minimal.pdf}}
\subfloat[(b) Ordered]{\includegraphics[width=7cm]{data/give2-minimal.pdf}}
  \caption{Results for the unordered and ordered minimal GIVE domains with grid
  height $h=20$. The horizontal axis is the grid width, $b = 2n$. The
  vertical axis is the total runtime in seconds.}
  \label{fig:give-runtime-minimal}
\end{figure}

@@

Results for the $h=20$, $n=5$ case with $w$ ranging from $1$ to $70$ are
shown in Figure~\ref{fig:give-extracells}. As in Experiment~2, FF again
runs out of memory, this time at $w=17$, while SGPLAN easily solves inputs
beyond $w=70$. As in Experiment~2, our implementation of GraphPlan is
unable to generate any of these plans. Unlike Experiment 2, however, both
FF and SGPLAN now spend a substantial proportion of their time on
grounding. In SGPLAN, this translates to a ``parsing time'' (which we
assume includes grounding) which grows from 180 ms to 21.7 seconds as $w$
grows from $1$ to $75$. The rest of the runtime, which also includes the
search time, only grows from 400 ms to 2.3 seconds. This difference is
particularly dramatic given that the actual optimal plan in each case is an
identical plan of about 100 steps (i.e., the one we would have found in
Experiment 2 for the $h=20$, $n=5$ case). The planning times for these
instances are also concerning since times over a couple seconds will
negatively affect the overall response time of the system, which must react
in real time to user actions.

%\begin{figure}[t]
%  \centering
%  \includegraphics[width=0.75\columnwidth]{graph-exp3}
%  %\includegraphics[width=1\columnwidth]{pic-runtime-empty-world}
%  \caption{Results on the GIVE domain with junk
%    positions for $h=20$ and $n=5$. The horizontal axis is $w$.
%    The vertical axis is the runtime in seconds.}
%\end{figure}

\begin{figure}[t]
\subfloat[(a) Unordered]{\includegraphics[width=7cm]{data/give-extracells.pdf}}
\subfloat[(b) Ordered]{\includegraphics[width=7cm]{data/give2-extracells.pdf}}
  \caption{Results for the unordered and ordered GIVE domains with $h = 20$ and
  $n = 10$. The horizontal axis is the extra grid width $w$.
  The vertical axis is the total runtime in seonds.}
  \label{fig:give-extracells}
\end{figure}

\begin{figure}[t]
\subfloat[(a) Unordered]{\includegraphics[width=7cm]{data/give-button-unord.pdf}}
\subfloat[(b) Ordered]{\includegraphics[width=7cm]{data/give-button-ord.pdf}}
  \caption{Results for the unordered and ordered GIVE domains with a grid size
  of height 20 and width 40. The horizontal axis is the number of buttons $b$.
  The vertical axis is the runtime in seonds.}
  \label{fig:give-buttons}
\end{figure}
